---
title: "Data607 HW 13"
author: "Ritesh Lohiya"
date: "April 27, 2018"
output: html_document
---

#Read the DB password for from the file
```{r}
password = read.table("C:/ProgramData/MySQL/MySQL Server 5.7/Uploads/flights/pass.txt")
```

#install.packages('RMySQL',type='source')
#install.packages('mongolite',type='source')
```{r}
library(RMySQL)
library(DBI)
library(ggplot2)
library(mongolite)
```

#Connection to the MySQL:


```{r}
moviesdb = dbConnect(MySQL(), user='root', password=toString(password[1,1]), dbname='movies', host='localhost')
```

#List the fields in demo table:

```{r}
dbListFields(moviesdb, 'demo')
```

#List the fields in ratings table:

```{r}
dbListFields(moviesdb, 'ratings')
```

#Frequency of the ratings:

```{r}
freq_df<-dbGetQuery(moviesdb,'select movie_name, rating, count(rating) as count
from ratings
group by movie_name,rating
order by movie_name, rating;')
```

#View the frequency distribution:

```{r}
freq_df
```

#Joining the 2 tables and prepare the dataframes:

```{r}
movies_df<-dbGetQuery(moviesdb, 'select 
a.name, 
a.name_id, 
a.state, 
a.age,
b.movie_name,
b.rating
from demo a
left join ratings b
on a.name_id=b.name_id
order by b.rating
;')
```

#Contents of the dataframe

```{r}
head(movies_df)
```

#Writing from Dataframe to MongoDB:

```{r}
c=mongo(collection="movies_df", db="Movies")
c$insert(movies_df)
```

#Checking for distinct movie name

```{r}
c$distinct("movie_name")
```

#Checking for distinct name

```{r}
c$distinct("name")
```

#Count the data in MongoDB

```{r}
c$count()
```

Likewise we can do aggregate, find, info etc....

#Comparisons:

Advantages of NoSql Databases:

1. Highly and easily scalable
2. No Schema or Fixed Data model
3. Maintaining NoSQL Servers is Less Expensive
4. Lesser Server Cost and open-Source
5. Support Integrated Caching

Disadvantages of NoSql Databases: 

1. There are not many defined standards for NoSQL databases, so no two NoSQL databases are equal.
2. No Stored Procedures in mongodb (NoSql database).

Advantages of relational Databases:

1. Provide facility primary key, to uniquely identify the rows.
2. Each row contains a unique instance of data for the categories defined by the columns.
3. Declarative syntax.


Disadvantages of relational Databases:

1. Scalability: Users have to scale relational database on powerful servers that are expensive and difficult to handle. 
2. Handling tables across different servers is difficult .
3. Complexity: If your data doesn't fit into tables, then you need to design your database structure that will be complex and again difficult to handle.



